Computable Poincar\'e--Friedrichs constants for the $L^{p}$ de~Rham complex over convex domains and domains with shellable triangulations

### 2024-10-11 main.tex
remark on the recursive estimate

\title{Computable Poincar\'e--Friedrichs constants for the $L^{p}$ de~Rham complex over convex domains and domains with shellable triangulations}
\author{
    Th\'eophile Chaumont-Frelet\thanks{Inria Univ. Lille and Laboratoire Paul Painlev\'e, 59655 Villeneuve-d'Ascq, France, \texttt{theophile.chaumont@inria.fr}} \and
    Martin Werner Licht\thanks{\'Ecole Polytechnique F\'ed\'erale de Lausanne, CH-1015 Lausanne, Switzerland, \texttt{martin.licht@epfl.ch}} \and
    Martin Vohral\'ik\thanks{Inria, 48 rue Barrault, 75647 Paris, France \& CERMICS, Ecole des Ponts, 77455 Marne-la-Vall\'ee, France, \texttt{martin.vohralik@inria.fr}}
}

@@

>>>>

\title{Computable Poincar\'e--Friedrichs constants for the $L^{p}$ de~Rham complex over convex domains and domains with shellable triangulations}
\author{
    Th\'eophile Chaumont-Frelet\thanks{Inria Univ. Lille and Laboratoire Paul Painlev\'e, 59655 Villeneuve-d'Ascq, France, \texttt{theophile.chaumont@inria.fr}} \and
    Martin Werner Licht\thanks{\'Ecole Polytechnique F\'ed\'erale de Lausanne, CH-1015 Lausanne, Switzerland, \texttt{martin.licht@epfl.ch}} \and
    Martin Vohral\'ik\thanks{Inria, 48 rue Barrault, 75647 Paris, France \& CERMICS, Ecole des Ponts, 77455 Marne-la-Vall\'ee, France, \texttt{martin.vohralik@inria.fr}}
}
\date{}

@@

\begin{remark}
    \color{red}
    We briefly outline how  to obtain an estimate for the Poincar\'e--Friedrichs constant from the recursive estimate in Theorem~\ref{theorem:poincarefriedrichsestimate:grad}.
    The potential $w$ for the gradient $\nabla u$ satisfies 
        \| w \|_{L^{p}(T_{0})} \leq A_{0} \| \nabla u \|_{L^{p}(T_{0})},
        \| w \|_{L^{p}(T_{m})} \leq A_{m} \| \nabla u \|_{L^{p}(T_{m})} + B_{m} \| w \|_{L^{p}(T_{m-1})},
    where $A_{m}, B_{m} \geq 0$ are numbers and $T_{0}, T_{1}, \dots, T_{m-1}, T_{m}$ is a face path.
    Unwrapping the recursion for the norm over the $m$-th simplex, we thus get
    \begin{align}\label{math:fullrecursivesum}
        \| w \|_{L^{p}(T_{m})} 
        \sum_{\ell=0}^{m} \left( B_{m} \cdots B_{\ell+1} \right) A_{\ell} \| \nabla u \|_{L^{p}(T_{\ell})}
        =:
        \sum_{\ell=0}^{M} C_{m,\ell} \| \nabla u \|_{L^{p}(T_{\ell})}
    Here, $C_{m,\ell}$ is the coefficient of $\| \nabla u \|_{L^{p}(T_{\ell})}$, possibly zero, as it appears in the unwrapped recursive estimate of $\| w \|_{L^{p}(T_{m})}$. 
    The global Poincar\'e--Friedrichs inequality follows via H\"older's inequality:
        \| w \|_{L^{p}(\Omega)}^{p}
        \sum_{m=0}^{M}
        \| w \|_{L^{p}(T_{m})}^{p}
        \sum_{m=0}^{M}
        \left( \sum_{\ell'=0}^{M} C_{m,\ell'}^{q} \right)^{\frac p q}
        \sum_{\ell=0}^{M} 
        \| \nabla u \|_{L^{p}(T_{\ell})}^{p} 
            \sum_{m=0}^{M}
            \left( \sum_{\ell=0}^{M} C_{m,\ell}^{q} \right)^{\frac p q}
        \| \nabla u \|_{L^{p}(\Omega)}^{p} 
    where $q \in [1,\infty]$ satisfies $1 = 1/p + 1/q$ and with obvious modifications if $p=1$ or $p=\infty$. 
    In other words, the Poincar\'e--Friedrichs inequality is estimated by first taking the $q$-norm of the coefficients in the full sum~\eqref{math:fullrecursivesum} and then taking $p$-norm of these intermediate sums.
    \color{green}Hence 
        \| w \|_{L^{p}(\Omega)}^{p}
        \sum_{m=0}^{M}
        \| w \|_{L^{p}(T_{m})}^{p}
        \sum_{m=0}^{M}
        \sum_{\ell=0}^{M} 
        \left( \sum_{\ell'=0}^{M} C_{m,\ell'}^{q} \right)^{\frac p q}
        \delta_{m,\ell} \| \nabla u \|_{L^{p}(T_{\ell})}^{p} 
        \max_{0 \leq \ell \leq M} \left(
            \sum_{m=0}^{M}
            \left( \sum_{\ell'=0}^{M} C_{m,\ell'}^{q} \right)^{\frac p q}
            \delta_{m,\ell} 
        \| \nabla u \|_{L^{p}(\Omega)}^{p} 
            \sum_{m=0}^{M}
            \left( \sum_{\ell'=0}^{M} C_{m,\ell'}^{q} \right)^{\frac p q}
        \| \nabla u \|_{L^{p}(\Omega)}^{p} 
    Now, if $q \leq p$, that is, $2 \leq p$, then 
            \sum_{m=0}^{M}
            \left( \sum_{\ell'=0}^{M} C_{m,\ell'}^{q} \right)^{\frac p q}
            \sum_{\ell'=0}^{M}
            \left( \sum_{m=0}^{M} C_{m,\ell'}^{p} \right)^{\frac q p}
        \right)^{\frac 1 q}
    Instead if $p \leq q$, that is, $p \leq 2$, then 
            \sum_{m=0}^{M}
            \left( \sum_{\ell'=0}^{M} C_{m,\ell'}^{q} \right)^{\frac p q}
        \sum_{m=0}^{M}
        \left( \sum_{\ell'=0}^{M} C_{m,\ell'}^{q} \right)^{\frac 1 q}
        \sum_{m=0}^{M}
        \left( \sum_{\ell'=0}^{M} C_{m,\ell'}^{p} \right)^{\frac 1 p}
    So in any case, it is better than using the following Minkowski's inequality: 
        \| w \|_{L^{p}(\Omega)}
        \left( \sum_{m=0}^{M} \left( \sum_{\ell=0}^{M} C_{m,\ell} \| \nabla u \|_{L^{p}(T_{\ell})} \right)^{p} \right)^{\frac 1 p}
        \sum_{\ell=0}^{M}
        \left( \sum_{m=0}^{M} C_{m,\ell}^{p} \| \nabla u \|_{L^{p}(T_{\ell})}^{p} \right)^{\frac 1 p}
        \sum_{\ell=0}^{M}
        \left( \sum_{m=0}^{M} C_{m,\ell}^{p} \right)^{\frac 1 p}
\end{remark}
